Aircraft Wildlife Collisions

### 2021-07-20 draft_final.Rmd
Update draft_final.Rmd

```{r echo=FALSE, fig.asp=0.5}
birds_strike_phase <- ggplot(birds[!is.na(birds$phase_of_flt) & !is.na(birds$birds_struck),]) +
  aes(x = phase_of_flt, fill=birds_struck) +
  scale_fill_brewer(palette="Blues") +
  geom_bar() +
  coord_flip() +
  theme(legend.position="none", 
        axis.title.y=element_blank(),
        axis.title.x=element_blank(),
        plot.subtitle = element_text(hjust =1)) +
  theme.title+
  labs(xlab = "phase of flight",
       subtitle = "Number of collisions by phase of flight")

@@

### Birds struck out of birds seen
birds_struck_seen <- ggplot(birds[!is.na(birds$birds_seen) & !is.na(birds$birds_struck),]) +
  geom_mosaic(aes(x = product(birds_struck,birds_seen), fill=birds_struck)) +
  scale_fill_brewer(palette="Blues") +
  #scale_fill_manual(values=brewer.pal(5,"Blues"))+
  theme(
    axis.text.y=element_blank(), 
        axis.title.y=element_blank(),
        axis.ticks.y = element_blank(),
        axis.text.x = element_text(angle = 90),
        legend.position="left")+
  theme.title+
  labs(title = "Birds struck overview",
       subtitle = "bird struck out of birds seen")

@@

birds_strike_ac_mass <- ggplot(birds_struck_minorities)+
aes(x=ac_mass, fill=birds_struck)+
  #scale_fill_manual(values=c("#eff3ff", "#3182bd", "#08519c")) +
  scale_fill_manual(values=brewer.pal(5,"Blues")[c(1,4,5)]) +
  geom_bar(position = "fill") +
  geom_text(aes(label=ifelse(round(..count../ac_struck_sums[1:14],2) > 0.1,round(..count../ac_struck_sums[1:14],2) , "")),
            stat='count',
            size = 2.3,
            position=position_fill(vjust = 0.5))+
  theme.title+
  labs(subtitle = "Birds struck (subset) by aircraft mass")

@@

### 3.1.1 Height of collisions above ground

@@

## 3.2 Analysis of birds seen

@@

## 3.3 Influences when number of birds struck is less than birds seen

@@

## 3.4 Analysis of effect variable

@@

```{r echo=FALSE, fig.asp=0.5}

@@

birds_struck_effect / (birds_effect_acmass + birds_effect_seenYes)

>>>>

```{r echo=FALSE, fig.asp=0.5}
birds_strike_phase <- ggplot(birds[!is.na(birds$phase_of_flt) & !is.na(birds$birds_struck) & as.integer(birds$phase_of_flt)>2,]) +
  aes(x = phase_of_flt, fill=birds_struck) +
  scale_fill_brewer(palette="Blues") +
  geom_bar() +
  coord_flip() +
  theme(legend.position="none", 
        axis.title.y=element_blank(),
        axis.title.x=element_blank(),
        plot.subtitle = element_text(hjust =1)) +
  theme.title+
  labs(xlab = "phase of flight",
       subtitle = "Number of collisions by phase of flight")

@@

### Birds struck out of birds seen
birds_struck_seen <- ggplot(birds[!is.na(birds$birds_seen) & !is.na(birds$birds_struck),]) +
  geom_mosaic(aes(x = product(birds_struck,birds_seen), fill=birds_struck)) +
  #scale_fill_brewer(palette="Blues") +
  scale_fill_manual(values=c("#EFF3FF","#BDD7E7","#6BAED6","#3182BD","#08519C"))+
  theme(
    axis.text.y=element_blank(), 
        axis.title.y=element_blank(),
        axis.ticks.y = element_blank(),
        axis.text.x = element_text(angle = 90),
        legend.position="left")+
  theme.title+
  labs(title = "Birds struck overview",
       subtitle = "bird struck out of birds seen")

@@

birds_strike_ac_mass <- ggplot(birds_struck_minorities)+
aes(x=ac_mass, fill=birds_struck)+
  #scale_fill_manual(values=c("#eff3ff", "#3182bd", "#08519c")) +
  scale_fill_manual(values=brewer.pal(6,"Blues")[c(1,4,5)]) +
  geom_bar(position = "fill") +
  geom_text(aes(label=ifelse(round(..count../ac_struck_sums[1:14],2) > 0.1,round(..count../ac_struck_sums[1:14],2) , "")),
            stat='count',
            size = 2.3,
            position=position_fill(vjust = 0.5))+
  theme.title+
  labs(subtitle = "Birds struck (subset) by aircraft mass")

@@

\newpage
### 3.1.1 Height of collisions above ground

@@

\newpage
## 3.2 Analysis of birds seen

@@

\newpage
## 3.3 Influences when number of birds struck is less than birds seen

@@

\newpage
## 3.4 Analysis of effect variable

@@

```{r echo=FALSE, fig.asp=0.3}

@@

birds_struck_effect

```
```{r echo=FALSE, fig.asp=0.35}
(birds_effect_acmass + birds_effect_seenYes)
```
